My presentation

### 2020-09-23 datayanolja.Rmd
powerpoint hello world
failed powerpoint pptx

---
title: "Untitled"
author: "Victor"
date: "11/30/2019"
output: 
  powerpoint_presentation:
    reference_doc: tidyverse-template.pptx
---

@@

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

>>>>

---
title: My presentation
output: 
  powerpoint_presentation:
    reference_doc: data/slide guides_C_template.pptx
    slide_level: 3
---

@@

# Section Header

Hi

## Section header

Second
